\begin{song}{title=\predtitle \centering All Stars \\\large Smash
Mouth }  %% sem se napíše jméno songu a autor

\vspace*{.5cm}

\begin{centerjustified}
\vetsi
\sloka
^*{\z G}Somebo dy once ^{\z D}told me the ^{\z Ami}world is gonna ^{\z C}roll me

I ^{G}ain't the sharpest ^{\z D}tool in the ^{\z Ami}shed. ^{C}

She was ^*{G}loo king kinda ^{\z D}dumb with her ^{Ami}finger and her

^{C\z}Thumb in the ^{G\z}shape of an ^{D}'L' on her ^{Ami}forehead.  ^{C}

\phantom{.}


\refren[1]
^{G}Well the years start coming and they ^{D\z}don't stop coming

^{Ami\z}Back to the rules and I ^{C}hit the ground running

^{G}Didn't make sense not to ^{\z D}live for fun

Your ^{Ami\z}brain gets smart but ^{C}your head gets dumb.

^*{G}So~mu ch to do ^*{D}so~mu ch to see

So ^{Ami\z}what's wrong with taking the ^{C}back streets.

^{G}You'll never know if you ^{D}don't go.

^{Ami}You'll never shine if you ^{C}don't glow.



\refren[2]
^{G}Hey now you're an ^{C}All Star get ^{C^{\#}dim\z}your~game on, ^*{C}go~pl ay.

^{G\z}Hey now you're a ^{\z C}Rock Star get ^{C^{\#}dim\z}the~show on ^*{C}get~pai d.

^{G\z}And all that ^{C\z}glitters is ^{\z C^{\#}dim}gold~~

^{C\z}Only shooting ^{G}stars ^{F}break the mold.   ^{C}


\end{centerjustified}
\newpage
\begin{centerjustified}

\sloka
^{\z G}It's a cool place and they ^{D}say it gets colder

^{Ami}You're bundled up now ^{C\z}but wait 'til you get older.

But ^{G\z}the media men beg to ^{D\z}differ

Judging by the ^*{\z Ami}hole~i n the satellite ^{C\z}picture.


\phantom{.}

The ice we ^{G}skate is getting pretty ^{D\z}thin

The waters getting ^{Ami}warm so you might as well ^{C}swim.

My world's on ^{G}fire how about ^{D}yours

That's the ^{Ami\z}way~I~like it and I never get ^*{C}bor ed.


\refren[2]

\refren[2]

\sloka
^{G\z}Somebody once ^{D}asked, could you ^{\z Ami}spare some change ^{\z C}for gas

^{G\z}I~need to get myself ^{\z D}away from this ^{\z Ami}place.   ^{C}

^{G\z}I~said yep what a ^*{D}con cept I could ^{\z Ami}use~a little fuel ^{C}myself

And we ^*{G}cou ld all ^{\z D}use~a little ^{Ami}change.   ^{C}


\refren[1]

\refren[2]

\end{centerjustified}


\setcounter{Slokočet}{0}
\end{song}
