\begin{song}{title=\centering Always Look On The Bright Side Of Life \\\normalsize Monty Python  \vspace*{-0.3cm}}  %% sem se napíše jméno songu a autor
\moveright 3.3cm \vbox{      %Varianta č. 1  ---> Jeden sloupec zarovnaný na střed	

\sloka 
	Some ^{Ami\,\,\,}things in life are ^{D{\color{white}\_}}bad, they can ^{G{\color{white}\_\_}}really make you ^{Emi\,\,\,}mad.

	Other ^{Ami{\color{white}\_}}things just make you ^{D{\color{white}\_\_}}swear and ^{G{\color{white}\_\_}}curse.

	When you've ^{Ami{\color{white}\_}}chewing on life's ^{D{\color{white}\_\_\_}}gristle, don't ^{G{\color{white}\_\_\_}}grumble give a ^{Emi{\color{white}\_}}whistle.

	And ^{Ami\,\,}this'll help things turn out for the ^{D7\,\,\,}best.

\refren
	And ^{G{\color{white}\_\_}}always ^{Emi}look on the ^{Ami\,\,\,}bright ^{D7}side of ^{G}life ^{Emi\,Ami\,D7}.

	Always look on the light side of life.

\sloka
	If ^{Ami}life seems jolly ^{D{\color{white}\_\_\_}}rotten, there's ^{G{\color{white}\_\_\_\_}}something you've ^{Emi{\color{white}\_\_\_}}forgotten.

	and that's to ^{Ami\,\,}laugh and smile and ^{D{\color{white}\_\_}}dance and ^{G{\color{white}\_}}sing.
	
	When you've ^{Ami\,\,\,}feeling in the ^{D{\color{white}\_\_}}dumps don't, be ^{G\,\,\,}silly ^{Emi{\color{white}\_}}chumps.

	Just ^{Ami}purse your lips and whistle -- that's the ^{D7{\color{white}\_}}thing.

\refren
	And always look on the bright side of life

	Come on always look on the bright side of life


\sloka
	For life is quite absurd and death's the final word,

	you must always face the curtain with a bow.

	Forget about your sin -- give the audience a grin.

	Enjoy it -- it's your last chance anyhow.


\refren
	So always look on the bright side of death
	
	just before you draw your terminal breath

\sloka
	Life's a piece if shit when you look at it.

	Life's a laugh and death's a joke it's true.

	You'll see it's all a show, keep'em laughing as you go.

	Just remember that the last laugh is on you.

\refren
	And always look on the bright side of life
	
	Always look on the right side of life
	
	(Come on guys, cheer up)


/: ^{A}Always ^{F#mi}look on the ^{Hmi}right ^{E7}side of ^{A}life ^{F#mi\,Hmi\,E7} :/




}
\setcounter{Slokočet}{0}
\end{song}
