\begin{song}{title=\predtitle \centering Cigarette Daydreams \\\large Cage The Elephant  \vspace*{-1.0cm}}  %% sem se napíše jméno songu a autor

\begin{centerjustified}
\velky

\sloka
^{D}Did you stand there all ^{Dmaj7}alone?

Oh ^{Emi\z}I~cannot ^{G}explain what's ^{A \z}going down.

I can see you standing next to me

In and out somewhere else right now.

^{D}You sigh, ^{Dmaj7 \z}look away ^{Hmi}

^{G}I can see it ^{A \z}clear as ^{\z D}day.

Close your eyes, ^{Dmaj7\z}so~afraid ^{Hmi}

^{G}Hide behind that ^{A \z}baby ^{D \z}face.

Do do do ^{Dmaj7\z}~do do do ^{Hmi Emi}

\refren[1]
^{Hmi \z}You can drive ^{D \z}all ^{\z G}night

Looking for the ^{F#m \z}answers in the pouring ^{\z Hmi}rain.

You wanna ^{\z D}find peace of ^{\z G}mind

^{F#m \z}Looking for the answer.

^{D Dmaj7 Emi G A}

\sloka
Funny how it seems like yesterday

As I recall you were looking out of place.

Gathered up your things and slipped away

No time at all I followed you into the hall.

Cigarette daydream

You were only seventeen

So sweet with a mean streak

Nearly brought me to my knees.

Do do do do do do

\refren[1]
You can drive all night

Looking for the answers in the pouring rain.

You wanna find peace of mind

Looking for the answer.

\end{varwidth}\mezisloupci\begin{varwidth}[t]{0.48\textwidth}\setlength{\parindent}{0.45cm}

\refren[2]
^{Hmi}If we can find a ^{D \z}reason, a reason to

change ^{G}

^{F#m \z}Looking for the answer.

^{Hmi}If you can find a ^{D \z}reason, a reason to

stay ^{G}

^{F#m \z}Standing in the pouring rain. ^{Emi}


^{A}Do do do do do ^{Emi}

Do do ^{D}do do ^{A}do do do ^{Emi}

Do do ^{A}do do do do do ^{Emi}

Do do ^{Hmi}do do ^{G}do do do ^{A}

\refren[1]
You can drive all night

Looking for the answers in the pouring

rain.

You wanna find peace of mind

^{F#m}Looking for the ^{Hmi}answer.

\refren[1]
If we can find a reason, a reason to

change

Looking for the answer.

If you can find a reason, a reason to

stay

Standing in the pouring rain.

\end{centerjustified}



\setcounter{Slokočet}{0}
\end{song}


