<<<<<<< HEAD
\documentclass[../main.tex]{subfiles}

\chapter*{Orlice}

\noindent\hspace{0.15\linewidth}
\begin{minipage}{0.7\linewidth}
\begin{song}{title=Hallelujah (Leonard Cohen / Jeff Buckley)}

\begin{verse}[numbered]
	I ^{C}heard there was a ^{Am}secret chord\\
	That ^{C}David ^{Am}played and it pleased the lord\\
	But^{F} you don't really ^{G}care for music, ^{C}do you?  ^{G}\\
	Well it ^{C}goes like this the ^{F}fourth, the ^{G}fifth\\
	The ^{Am}minor fall and the ^{F}major lift\\
	The ^{G}baffled king ^{E7}composing halle^{Am}lujah\\
\end{verse}

\begin{verse}[numbered]
	Halle^{F}lujah, hallel^{Am}ujah, halle^{F}lujah, hal^{C}lelu-u-^{G}u-u-^{C}jah .... 
\end{verse}

\begin{verse}[numbered]
	Your faith was strong, but you needed proof,\\
	you saw her bathing on the roof,\\
	her beauty and the moonlight overthrew you.\\
	She tied you to a kitchen chair,\\
	she broke your throne, and she cut your hair,\\
	and from your lips she drew the Hallelujah!\\
\end{verse}

\begin{verse}[numbered]	
	R:
\end{verse}

\begin{verse}[numbered]	
	You say I took the name in vain,\\
	I don’t even know the name,\\
	but if I did, well really, what’s it to you?\\
	There’s a blaze of light in every word,\\
	it doesn’t matter which you heard,\\
	the holy or the broken Hallelujah!\\
\end{verse}

\begin{verse}[numbered]	
	R:
\end{verse}

\begin{verse}[numbered]	
	Baby, I’ve been here before,\\
	I know this room, I’ve walked this floor,\\
	I used to live alone before I knew you.\\
	I’ve seen your flag on the marble arch,\\
	but love is not a victory march,\\
	it’s a cold and it’s a broken Hallelujah!\\
\end{verse}

\begin{verse}[numbered]	
	R:
\end{verse}

\begin{verse}[numbered]	
	There was a time you let me know,\\
	what’s really going on below,\\
	but now you never show it to me, do you?\\
	But I remember, when I moved in you,\\
	and the holy dove was moving too,\\
	and every breath we drew was Hallelujah!\\
\end{verse}

\begin{verse}[numbered]
	R:
\end{verse}

\begin{verse}[numbered]	
	Maybe there’s a God above,\\
	but all I’ve ever learned from love\\
	was how to shoot at someone who outdrew you.\\
	But it’s not a cry that you hear at night,\\
	it’s not somebody who’s seen the light,\\
	it’s a cold and it’s a broken Hallelujah!\\
\end{verse}

\begin{verse}[numbered]
	I did my best, it wasn’t much,\\
	I couldn’t feel, so I tried to touch,\\
	I’ve told the truth, I didn’t come to fool you.\\
	And even though it all went wrong,\\
	I’ll stand before the Lord of Song\\
	with nothing on my tongue but Hallelujah!\\
\end{verse}

\begin{verse}[numbered]
	R: (2×)
\end{verse}


\end{song}
\end{minipage}




%\begin{verse}[numbered]
%^{D}Do Ameriky jezděj Parníky,\\
%když tam přijdeš, zdá se ti to ^{A7}všecko veliký,\\
%^{\phantom{S}}je to fakticky tuze praktický  \\
%když tam přijdeš, umět anglic^{D}ky. \\
%\end{verse}
%\begin{verse*}
%Refrain:
%^{D}Dobrou noc - good night, ^{A7}výborně - all right,\\
%Konrád White, už je off^{D}side (housemister - Dally sister!) \\
%^{D}Dneska je today, ^{A7}dobrý den - good day,\\
%já jsem byl taky chu^{D}dej. \\ 
%^{G}His Master's Voice, Yankee Doo^{G}dle,\\ \\
%^{En7}máš apetit? (mám) ^{A7}vem si štrůdl! (do pusy)\\
%^{D}Sto kilo je cent, ^{A7}patent je patent,\\
%husa v troubě happy^{D}end.
%\end{verse*}
%\begin{verse}[numbered]
%Co Buffalo Bill vrazil do kobyl,\\
%za to by si bejval byl koupil automobil,\\
%cowboy na koni už se nehoní,\\
%přestože mu Fordka nevoní.\\
%\end{verse}
%\begin{verse*}
%Refrain
%\end{verse*}
%\begin{verse}[numbered]
%Mám na západě chajdu v Nevadě,\\
%zlatou žílu v Arizoně, doly v Kanadě,\\
%babička na mě šetří v Panamě\\
%a já si tu žiju náramě!\\
%\end{verse}
=======
%\documentclass[../main.tex]{subfiles}

\begin{song}{title=\centering Hallelujah \\\normalsize Leonard Cohen / Jeff Buckley \vspace*{-0.3cm}}  %% sem se napíše jméno songu a autor
\moveright 1cm \vbox{      %Varianta č. 1  ---> Jeden sloupec zarovnaný na střed
\begin{minipage}[t]{0.48\textwidth}\setlength{\parindent}{0.45cm}  %Varianta č. 2 --> Dva sloupce
\sloka
	I ^{C}heard there was a ^{Am}secret chord  
	
	That ^{C}David ^{Am}played and it pleased the lord  
	
	But^{F} you don't really ^{G}care for music, ^{C}do you?^{G}  
	
	Well it ^{C}goes like this the ^{F}fourth, the ^{G}fifth  
	
	The ^{Am}minor fall and the ^{F}major lift  
	
	The ^{G}baffled king ^{E7}composing halle^{Am}lujah  
	

\refren
^{F}Hallelujah, ^{Am}hallelujah, ^{F}hallelujah,

 ^{C G C}hallelu-u-u-u-jah \dots

\sloka
	Your faith was strong, but you needed proof,  
	
	you saw her bathing on the roof,  
	
	her beauty and the moonlight overthrew you.  
	
	She tied you to a kitchen chair,  
	
	she broke your throne, and she cut your hair,  
	
	and from your lips she drew the Hallelujah!  


\refren

\sloka
	You say I took the name in vain,  
	
	I don't even know the name,  
	
	but if I did, well really, what's it to you?  
	
	There's a blaze of light in every word,  

	it doesn't matter which you heard,  
	
	the holy or the broken Hallelujah!  
	

\refren

\sloka
	Baby, I've been here before,  
	
	I know this room, I've walked this floor,  
	
	I used to live alone before I knew you.  
	
	I've seen your flag on the marble arch,  
	
	but love is not a victory march,  
	
	it's a cold and it's a broken Hallelujah!  


\end{minipage}\begin{minipage}[t]{0.48\textwidth}\setlength{\parindent}{0.45cm}  % V případě varianty č.2 jde odsud text do pravé části
\vspace*{0.6cm}
\refren

\sloka
	There was a time you let me know,   
	
	what's really going on below,   
	
	but now you never show it to me, do you?   
	
	But I remember, when I moved in you,   
	
	and the holy dove was moving too,   
	
	and every breath we drew was Hallelujah!   
	
\refren

\sloka
	Maybe there's a God above,   
	
	but all I've ever learned from love   
	
	was how to shoot at someone who outdrew you.   
	
	But it's not a cry that you hear at night,   
	
	it's not somebody who's seen the light,   
	
	it's a cold and it's a broken Hallelujah!   
	
\sloka
	I did my best, it wasn't much,   
	
	I couldn't feel, so I tried to touch,   
	
	I've told the truth, I didn't come to fool you.   
	
	And even though it all went wrong,   
	
	I'll stand before the Lord of Song   
	
	with nothing on my tongue but Hallelujah!   
	


\refren

\end{minipage}   %Součást druhé varianty
}
\setcounter{Slokočet}{0}
\end{song}
>>>>>>> 297b9f5e9c401ffde5e9fed7fb559aeac7b7a183
