\begin{song}{title=\predtitle\centering Hero Of War\\\large Rise Against \vspace*{-0.3cm}}  %% sem se napíše jméno songu a autor
\begin{centerjustified}
\vetsi

\begin{varwidth}[t]{0.48\textwidth}\setlength{\parindent}{0.45cm}  %Varianta č. 2 --> Dva sloupce

\sloka
He said, ^{E}``Son,

Have you see the ^{\z G^{\#}m}world?

Well, what would ^{A}you~say

If I said that you ^{\z E}could?

Just carry this ^{A}gun and you’ll even get

^{E}paid.''

I said, ``That sounds pretty ^{\z B}good.''

\sloka
Black leather boots

Spit-shined so bright

They cut off my hair but it looked

alright.

We marched and we sang,

We all became friends

As we learned how to fight.

\refren
A hero of ^{C^{\#}m\z}war,~~

Yeah that’s what I’ll ^{A}be

And when I come ^{E}home

They’ll be damn proud ^{B}of~me.

I’ll carry this ^{C^{\#}m}flag

To the grave if I ^{A}must

Because it’s flag that I ^{E}love

And a flag that I ^{B}trust.

\end{varwidth}\mezisloupci\begin{varwidth}[t]{0.48\textwidth}\setlength{\parindent}{0.45cm}%\vspace*{0.55cm}  % V případě varianty č.2 jde odsud text do pravé části

\sloka
I kicked in the door,

I yelled my commands.

The children, they cried

But I got my man.

We took him away

A bag over his face

From his family and his friends.

\sloka
They took off his clothes,

They pissed in his hands.

I told them to stop

But then I joined in.

We beat him with guns

And batons not just once

But again and again.

\refren

\sloka
She walked through bullets and haze,

I asked her to stop,

I begged her to stay,

But she pressed on.

So I lifted my gun

And I fired away.

\sloka
And the shells jumped through the smoke

And into the sand

That the blood now had soaked.

She collapsed with a flag in her hand

A flag white as snow.

\refren

\dots And I brought home that flag,

Now it gathers dust

But it's a flag that I love

The only flag that I trust.


He said, ``Son, have you seen the

world?

Well what would you say, if I said that

you could?''

\end{varwidth}

\end{centerjustified}
\setcounter{Slokočet}{0}
\end{song}
