\begin{song}{title=\predtitle\centering Little Talks \\\large Of Monsters and Men  \vspace*{-0.3cm}}  %% sem se napíše jméno songu a autor
\begin{centerjustified}
\vetsi

%^{$\4 \times$ Ami F C G}
\kapodastr{1}

\begin{minipage}{0.75\textwidth}
\sloka
    ^{Ami \z}I~don't like ^{F \z}walking around this ^{C}old and empty house

    So ^{Ami \z}hold~my hand, I'll ^{F \z}walk with you, my ^{C \z}dear.
\end{minipage}
\begin{minipage}{0.20\textwidth}
\vspace*{0.3cm}
\refren[2] $2 \times $

\refren[1] $2 \times $
\end{minipage}

    The ^{Ami \z}stairs creak ^{F \z}as you sleep, it's ^{C \z}keeping me awake

    It's the ^{Ami \z}house telling ^{F \z}you to close your ^{C \z}eyes

    And ^{Ami \z}some days ^{F}I can't even ^{C \z}dress myself

    It's ^{Ami \z}killing me to ^{F \z}see you this ^{C}way.

\refren[1]
    'Cause though the ^{Ami \z}truth may ^{F \z}vary

    this ^{C}ship will ^{G \z}carry our ^{Ami \z}bodies ^{F \z}safe to ^{C \z}shore. (\dots ^{G}Hey!) ^{\, $(4\times )$ Ami F C G}

\sloka
    There's an old voice in my head that's holding me back.

    Well tell her that I miss our little talks

    Soon it will be over and buried with our past.

    We used to play outside when we were young (and full of life and full of love).

    Some days I don't know if I am wrong or right

    Your mind is playing tricks on you, my dear.


\vspace*{-0.3cm}
\refren[1]

\vspace*{-0.3cm}
\refren[2]
    Don't ^{Ami \z}listen to a ^*{F \z C \,}word~I~s ay. ^{G}Hey!

    The ^{Ami \z}screams all ^{F \z}sound the ^{C \z}same. ^{G}Hey!

    Though the ^{Ami \z}truth may ^{F \z}vary

    this ^{C}ship will ^{G \z}carry our ^{Ami \z}bodies ^{F \z}safe to ^{C \z}shore. (\dots ^{G}Hey!)  ^{\, $(4\times )$ Ami F C G}

\sloka
    You're gone, gone, gone away I watched you disappear.

    All that's left is a ghost of you.

    Now we're torn, torn, torn apart, there's nothing we can do

    Just let me go we'll meet again soon.

    Now wait, wait, wait for me please hang around.

    I'll see you when I fall asleep. Hey!





\end{centerjustified}
\setcounter{Slokočet}{0}
\end{song}
