\begin{song}{title=\predtitle\centering One \\\large Johnny Cash  \vspace*{-.3cm}}  %% sem se napíše jméno songu a autor
\begin{centerjustified}
\begin{varwidth}[t]{0.57\textwidth}\setlength{\parindent}{0.45cm}  %Varianta č. 2 --> Dva sloupce

\sloka
 	^{Ami\z}Is~it getting ^{D\z}better

	^{F\z}Or do you feel the ^{G\z}same?

	^{ Ami}Will it make it ^{D\z}easier on you now

	^{F\z}If you've got someone to ^{\z G}blame?


\refren
	You said ^{C}one love ^{ Ami}

	One life ^{F}

	When it's one need ^{C}

	In the night.
  
	One love, we get to ^{ Ami\,\,}share it.

	It ^{F\z}leaves you, baby, if you don't

	^{C\z}care for it.


\sloka
	Did I disappoint you

	Or leave a bad taste in your mouth?

	You act like you never had love

	And you want me to go without.

\refren
	Well it's ^{C}too late ^{ Ami}

	Tonight ^{F}

	To drag the past out ^{C}

	Into the light. ^{C}

	We're one but we're ^{ Ami}not the same.

	We get to ^{ F}carry each other,

	^{C}Carry each other.

	One.

\end{varwidth}\mezisloupci\begin{varwidth}[t]{0.55\textwidth}\setlength{\parindent}{0.45cm}
\vspace*{0.3625cm}  % V případě varianty č.2 jde odsud text do pravé části

\sloka
	Have you come here for forgiveness?

	Have you come to raise the dead?

	Have you come here to play Jesus

	To the lepers in your head?

\refren
	Did I ask ^{ C}too much? ^{ Ami}

	More than a lot? ^{ F}

	You gave me nothing, now
	   
	^{ C}It's all I got.

	We're one but we're ^{ Ami}not the same.

	Well, we ^{ F}hurt each other and we ^{ C}do

	it again.

\refren
	You said ^{ C \z}love is a temple.

	^{ Ami\,\,}Love the higher law.

	Love is a temple.	

	Love the higher law.

	^{ C \z}You ask me to enter

	^{ G\,\,}But then you make me crawl

	I can't be holding on ^{ F}
                  
	To what you've got

	When all you've got is ^{ C}hurt.


\end{varwidth}
\end{centerjustified}
\newpage
\begin{centerjustified}
\begin{varwidth}[t]{0.57\textwidth}\setlength{\parindent}{0.45cm}  %Varianta č. 2 --> Dva sloupce



\end{varwidth}\mezisloupci\begin{varwidth}[t]{0.55\textwidth}\setlength{\parindent}{0.45cm}

\refren
	One love, ^{ Ami}

	One blood, ^{ F}

	One life, ^{ C}
 
	You've got to do what you should.

	One life with ^{ Ami\,\,}each other. ^{ F}
 
 	Sisters, ^{ C}
 
	Brothers.
   
	One life, but we're ^{ Ami}not the same.

	We get to ^{ F}carry each other,

  	^{ C{\color{white}\_\_}}Carry each other,

  	/: ^{ \,\,C\,\,Ami}One ^{ \,\,F\,\,C}One. :/


\end{varwidth}
\end{centerjustified}

\setcounter{Slokočet}{0}
\end{song}
