%\documentclass[../main.tex]{subfiles}

\begin{song}{title=\centering Sound Of Silence \\\normalsize Simon \& Garfunkel  \vspace*{-0.3cm}}  %% sem se napíše jméno songu a autor
\moveright 3.3cm \vbox{      %Varianta č. 1  ---> Jeden sloupec zarovnaný na střed

\phantom{\,}

Capo 5
	
\sloka
   ^{Ami\,}Hello darkness my old ^{G{\color{white}\_\_}}friend
   
   I've come to talk with you ^{Ami\,}again
   
   because a vision softly ^{F{\color{white}\_}\,C{\color{white}\_}}creeping
   
   left it seeds while I was ^{F{\color{white}\_}\,C{\color{white}\_}}sleeping.
   
   And the ^{F{\color{white}\_\_}}vision that was planted in my ^{C\,{\color{white}\_}}brain 
   
   still ^{Ami}remains within the ^{G{\color{white}\_\_}}sound of ^{Ami{\color{white}\_\_}}silence.

\sloka
   In restless dreams I walked alone, 
   
   narrow streets of cobble-stone ,
   
   'neath the halo of a street lamp 
   
   I turned my collar to the cold and damp.
   
   When my eyes were stabbed by the flash of a neon light 
   
   that spilt the night and touched the sound of silence.
   
\sloka
   And in the naked light I saw 
   
   ten thousand people maybe more 
   
   People talking without speaking,
   
   people hearing without listening,
   
   people writing songs that voices never share,
   
   and no one dare disturb the sound of silence.
   
\sloka
   \uv{Fools!} said I \uv{you do not know
   
   silence like a cancer grows 
   
   hear my words that I might teach you 
   
   take my arms that I might reach you.} 
   
   But my words like silent raindrops fell 
   
   and echoed in the wells of silence. 
   
\sloka
   And the people bowed and prayed 
   
   to the neon god they made 
   
   and the sign flashed out its warning 
   
   in the words that it was forming and the sign said: 
   
   \uv{The words of the prophets are written on the subway walls 
   
   and tenament halls} and whisper'd in the sound of silence. 
   

}
\setcounter{Slokočet}{0}
\end{song}
