\begin{song}{title=\predtitle\centering Space Oddity \\\large David Bowie  \vspace*{-0.3cm}}  %% sem se napíše jméno songu a autor

\nejvetsi
\begin{centerjustified}

\sloka 
	^{C\z}Ground control to Major ^{Emi\z}Tom, ^{C\z}Ground control to Major ^{Emi\z}Tom:

	^{Ami}Take your ^{Am7/G\z}protein~pills and ^{D7}put your helmet on.

	^{C\z}Ground control to Major ^{Emi\,}Tom:  ^{C\z}Commencing countdown engine's ^{Emi\z}on~~

	^{Ami\z}Check ^{Ami7/G}ignition and may ^{D7\,\,}God's love be with you

	^{C\z }This is ground control to Major ^{E7}Tom, you've really made the ^{F\z}grade!

	And the ^{Fmi\z }papers want to ^{C\z }know whose shirts you ^{F\z}wear,

	now it's ^{Fmi\,}time to leave the ^{C{\z}}capsule if you ^{F{\z}}dare.

	^{C{\z}}This is Major Tom to ground ^{\,E7}control, I'm stepping through the ^{F{\z}}door

	And I'm ^{Fmi{\z}}floating in the ^{C\z}most peculiar ^{F\,\,\,}way 

	and the ^{Fmi\,}stars look very ^{C\z}different ^{F}today

	For ^{Fmaj7}here am I ^{Em7}sitting in a tin ^{Fmaj7\:}can,~far~above the ^{Em7}world

	^{Bmaj7}Planet Earth is ^{Ami}blue and there's ^{G{\z}}nothing I can ^{F}do.

	\phantom{.}

	\phantom{.}

/: \writechord{C\,F\,G\,A} :/ \writechord{Fmaj7\,Emi7\,A\,C\,D\,E}

\end{centerjustified}
\newpage
\begin{centerjustified}

\sloka
	^{C{\z}}Though I'm passed one hundred thousand ^{E7{\z}}miles, I'm feeling very ^{F\,\,}still

	And I ^{Fmi\,}think my spaceship ^{C{\z}}knows which way to ^{F}go,

	tell my ^{Fmi}wife I love her ^{C\,\,\,}very much, she ^{F{\z}}knows.

	^{G\z}Ground control to ^{E7\,\,}Major Tom:

	Your ^{Ami{\z}}circuit's dead, there's ^{Am7/G\,\,\,}something wrong.

	Can you ^{D7\,\,}hear me Major Tom? Can you ^{C\,\,}hear me Major Tom? 

	Can you ^{G\,\,}hear me Major Tom? Can you\dots

	^{Fmaj7\z}Here~am I ^{Emi7\,\,}floating in my tin ^{Fmaj7\,}can,~far~above the ^{Emi7}moon.

	^{Bmaj7}Planet Earth is ^{Ami}blue and there's ^{G\z}nothing I can ^{F}do.


\end{centerjustified}
\setcounter{Slokočet}{0}
\end{song}
