\begin{song}{title=\predtitle\centering Hallelujah \\\large Leonard Cohen / Jeff Buckley \vspace*{-0.3cm}}  %% sem se napíše jméno songu a autor
\begin{centerjustified}

\begin{varwidth}[t]{0.48\textwidth}\setlength{\parindent}{0.45cm}  %Varianta č. 2 --> Dva sloupce

\sloka
	I ^{C{\color{white}\_\_}}heard there was a ^{Ami}secret chord  
	
	That ^{C{\color{white}\_}}David played and it ^{Ami}pleased the 

	lord  
	
	But ^{F}you don't really ^{G}care for music, ^{C}do 

	you?^{G}  
	
	Well ^{C}it goes like this: the ^{F{\color{white}\_\_}}fourth, the 

	^{G}fifth,  
	
	The ^{Ami}minor fall and the ^{F{\color{white}\_\_}}major lift,  
	
	The ^{G{\color{white}\_\_}}baffled king ^{E7}composing Halle^{Ami}lujah!  
	

\refren
	^{F}Hallelujah, ^{Ami}hallelujah, ^{F}hallelujah,
	
	^{C}halleluuu - u - ^{G}uuu - u - ^{C}jah\elipsa.\elipsa.\elipsa.  

\sloka
	Your faith was strong, but you needed proof,  
	
	you saw her bathing on the roof,  
	
	her beauty and the moonlight overthrew 

	you.  
	
	She tied you to a kitchen chair,  
	
	she broke your throne, and she cut your 

	hair,  
	
	and from your lips she drew the 

	Hallelujah!  


\refren


\sloka
	You say I took the name in vain,  
	
	I do not even know the name,  
	
	but if I did, well really, what's it to you?  
	
	There's a blaze of light in every word,  

	it doesn't matter which you heard,  
	
	the holy or the broken Hallelujah!  
	

\refren



\end{varwidth}\mezisloupci\begin{varwidth}[t]{0.5\textwidth}\setlength{\parindent}{0.45cm}  % V případě varianty č.2 jde odsud text do pravé části
\vspace*{0.375cm}
\sloka
	Baby, I have been here before,  
	
	I know this room, I've walked this floor,  
	
	I used to live alone before I knew you.  
	
	I've seen your flag on the marble arch,  
	
	but love is not a victory march,  
	
	it's cold and it's a broken Hallelujah!  

\refren

\sloka
	There was a time you let me know,   
	
	what's really going on below,   
	
	but now you never show it to me, do you?   
	
	But I remember, when I moved in you,   
	
	and the holy dove was moving too,   
	
	and every breath we drew was Hallelujah!   
	
\refren

\sloka
	Maybe there's a God above,   
	
	but all I've ever learned from love   
	
	was how to shoot at someone who 

	outdrew you.   
	
	But it's not a cry that you hear at night,   
	
	it's not somebody who's seen the light,   
	
	it's a cold and it's a broken Hallelujah!   
	
\sloka
	I did my best, it wasn't much,   
	
	I couldn't feel, so I tried to touch,   
	
	I've told the truth, I didn't come to fool 

	you.   
	
	And even though it all went wrong,   
	
	I'll stand before the Lord of Song   
	
	with nothing on my tongue but 

	Hallelujah!   
	

\refren

\end{varwidth}   %Součást druhé varianty

\end{centerjustified}
\setcounter{Slokočet}{0}
\end{song}
