\begin{song}{title=\predtitle\centering Lemon Tree \\\large Fool's Garden  \vspace*{-0.3cm}}  %% sem se napíše jméno songu a autor
\begin{centerjustified}

\begin{varwidth}[t]{0.48\textwidth}\setlength{\parindent}{\pindent}  %Varianta č. 2 --> Dva sloupce

\sloka
I'm ^{Emi\z}sittin' here in the ^{Hmi}boring room,

It's ^{Emi}just another rainy Sunday 

^{Hmi}afternoon.

I'm ^{Emi\z}wasting my time I got ^{Hmi}nothing 

to do,

I'm ^{Emi\z}hangin' aroud I got ^{Hmi}waitin' for you.

But ^{Ami\z}nothing ever happens^{H}

And I ^{Emi\z}wonder.

\sloka
I'm drivin' aroud in my car,

I'm drivin' too fast, I'm drivin' too far,

I'd like to change my point of view,

I feel so lonely I'm waiting for you.

But nothing ever happens.

\refren
^{G\z}I~wonder how, ^{D\z}wonder why

^{Emi\z}Yesterday you told me 'bout the ^{Hmi}blue

 ^{\phantom{.}}blue sky

And ^{C}all that I can ^{D}see

Is just a yellow ^{G\z}lemon tree.^{D} 

I'm ^{G\z}turnin' my head ^{D}up and down.

^{Emi\z}I'm~turnin', turnin', turnin', ^{Hmi}turnin',

 ^{\phantom{.}}turnin' around

And ^{C}all that I can ^{D}see

Is just a yellow ^{G\z}lemon tree.^{D} 

\end{varwidth}\mezisloupci\begin{varwidth}[t]{0.48\textwidth}\setlength{\parindent}{\pindent}  % V případě varianty č.2 jde odsud text do pravé části
\vspace*{-0.110cm}
\sloka
^{4(Emi Hmi) Ami H Emi}Sing\,dip,\,ta\,da\,da\,dap\,di\,dap\,dam\elipsa.\elipsa.\elipsa.

\sloka
I'm sittin' here, I miss the power,

I'd like to go out, takin' a shower.

But there's a heavy cloud inside my head,

I feel so tired put myself into bed

Where nothing ever happens

And I wonder.

\sloka
^{H\z}Isolation ^{Emi}is not good for me.

^{D\z}Isolation, ^{G}I don't want to

^{H}sit on a lemon tree.

\sloka
I'm steppin' around in a desert of joy,

Baby, anyhow I get another toy

And everything will happen

And you'll wonder.

\refren
%^{G}I wonder how\elipsa\dots \\

\refren
%^{G}I wonder how\elipsa\dots \\


\dots\,and all that I can see --

and all that I can see --

and all that I can see 

Is just a yellow lemon tree.

\end{varwidth}

\end{centerjustified}
\setcounter{Slokočet}{0}
\end{song}
