\begin{song}{title=\centering One \\\normalsize Johnny Cash  \vspace*{-0.3cm}}  %% sem se napíše jméno songu a autor

%\renewcommand{\baselinestretch}{0.4}


\vspace*{-1cm}
\moveright 0.0cm \vbox{      %Varianta č. 1  ---> Jeden sloupec zarovnaný na střed	

\begin{minipage}[t]{0.55\textwidth}\setlength{\parindent}{0.45cm} %Varianta č. 2 --> Dva sloupce

{\parskip=0pt
%\small
\normalsize

\sloka 
 	^{\small Ami}Is it getting ^{\small D{\color{white}\_\_\_}}better

	^{\small F\,}Or do you feel the ^{\small G{\color{white}\_\_\_}}same?

	^{\small Ami}Will it make it ^{\small D{\color{white}\_\_\_}}easier on you now

	^{\small F\,\,}If you've got someone to ^{\small {\color{white}\_\_\_}G}blame?

   
\refren
	You said ^{\small C}one love ^{\small Ami}

	One life ^{\small F}

	When it's one need ^{\small C}
         
	In the night.
  
	One love, we get to ^{\small Ami\,\,}share it.

	It ^{\small F{\color{white}\_\_}}leaves you, baby, if you don't ^{\small C{\color{white}\_\_}}care for it.   


\sloka
	Did I disappoint you

	Or leave a bad taste in your mouth?

	You act like you never had love

	And you want me to go without.


\refren
	Well it's ^{\small C}too late ^{\small Ami}

	Tonight ^{\small F}

	To drag the past out ^{\small C}

	Into the light. ^{\small C}

	We're one but we're ^{\small Ami}not the same.

	We get to ^{\small F}carry each other,

	^{\small C}Carry each other.
 
	One.

\sloka    
	Have you come here for forgiveness?

	Have you come to raise the dead?

	Have you come here to play Jesus

	To the lepers in your head?

}
\end{minipage}\begin{minipage}[t]{0.55\textwidth}\setlength{\parindent}{0.45cm}\vspace*{0.0cm}  % V případě varianty č.2 jde odsud text do pravé části
{\parskip=0pt

\refren       
	Did I ask ^{\small C}too much? ^{\small Ami}

	More than a lot? ^{\small F}

	You gave me nothing, now
	   
	^{\small C}It's all I got.

	We're one but we're ^{\small Ami}not the same.

	Well, we ^{\small F}hurt each other and we ^{\small C}do it again. 
 
\refren
	You said ^{\small C{\color{white}\_}}love is a temple.

	^{\small Ami\,\,}Love the higher law.

	Love is a temple.	

	Love the higher law.

	^{\small C{\color{white}\_}}You ask me to enter

	^{\small G\,\,}But then you make me crawl

	I can't be holding on ^{\small F}
                  
	To what you've got

	When all you've got is ^{\small C}hurt.
  
\refren
	One love, ^{\small Ami}

	One blood, ^{\small F}

	One life, ^{\small C}
 
	You've got to do what you should.

	One life with ^{\small Ami\,\,}each other. ^{\small F}
 
 	Sisters, ^{\small C}
 
	Brothers.
   
	One life, but we're ^{\small Ami}not the same.

	We get to ^{\small F}carry each other,

  	^{\small C{\color{white}\_\_}}Carry each other,

  	/: ^{\small \,\,C\,\,Ami}One ^{\small \,\,F\,\,C}One. :/


\normalsize

}
\end{minipage}
}
\setcounter{Slokočet}{0}
\end{song}
