\begin{song}{title=\predtitle\centering Space Oddity \\\large David Bowie  \vspace*{-0.3cm}}  %% sem se napíše jméno songu a autor
\begin{centerjustified}
\normalsize

\sloka 
	^{C{\color{white}\_\_\_}}Ground control to Major ^{Emi\,}Tom, ^{C{\color{white}\_\_}}Ground control to Major ^{Emi\,}Tom:

	^{Ami}Take your ^{Am7/G}protein pills and ^{D7}put your helmet on.

	^{C{\color{white}\_\_\_}}Ground control to Major ^{Emi\,}Tom:  ^{C{\color{white}\_\_\_\_\_}}Commencing countdown engine's ^{Emi}on

	^{Ami\,\,\,}Check ^{Ami7/G}ignition and may ^{D7\,\,}God's love be with you

	^{C{\color{white}\_}}This is ground control to Major ^{E7}Tom, you've really made the ^{F{\color{white}\_\_}}grade!

	And the ^{Fmi{\color{white}\_}}papers want to ^{C}{\color{white}\_\_}know whose shirts you ^{F{\color{white}\_}}wear, 

	now it's ^{Fmi\,}time to leave the ^{C{\color{white}\_\_}}capsule if you ^{F{\color{white}\_}}dare.

	^{C{\color{white}\_}}This is Major Tom to ground ^{\,E7}control, I'm stepping through the ^{F{\color{white}\_}}door

	And I'm ^{Fmi{\color{white}\_}}floating in the ^{C{\color{white}\_}}most peculiar ^{F\,\,\,}way 

	and the ^{Fmi\,}stars look very ^{C{\color{white}\_\_\_}}different ^{F}today
       
	For ^{Fmaj7}here am I ^{Em7}sitting in a tin can, ^{Fmaj7}far above the ^{Em7}world

	^{Bmaj7}Planet Earth is ^{Ami}blue and there's ^{G{\color{white}\_\_\_}}nothing I can ^{F}do.
	
	\phantom{.}

/: \textbf{C\,F\,G\,A} :/ \textbf{Fmaj7\,Em7\,A\,C\,D\,E}

 
\sloka
	^{C{\color{white}\_\_\_}}Though I'm passed one hundred thousand ^{E7{\color{white}\_}}miles, I'm feeling very ^{F\,\,}still

	And I ^{Fmi\,}think my spaceship ^{C\,{\color{white}\_\_}}knows which way to ^{F}go, 

	tell my ^{Fmi}wife I love her ^{C\,\,\,}very much, she ^{F{\color{white}\_\_}}knows.

	^{G{\color{white}\_\_\_}}Ground control to ^{E7\,\,}Major Tom: 

	Your ^{Ami{\color{white}\_}}circuit's dead, there's ^{Am7/G\,\,\,}something wrong.

	Can you ^{D7\,\,}hear me Major Tom? Can you ^{C\,\,}hear me Major Tom? 

	Can you ^{G\,\,}hear me Major Tom? Can you\dots

	^{Fmaj7}Here am I ^{Emi7\,\,}floating in my tin can, ^{Fmaj7}far above the ^{Emi7}moon.

	^{Bmaj7}Planet Earth is ^{Ami}blue and there's ^{G{\color{white}\_\_\_}}nothing I can ^{F}do.


\end{centerjustified}
\setcounter{Slokočet}{0}
\end{song}
